Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-10-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Sunday 22 October 2023 at home

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(plotly)
library(knitr)
library(rgl)
library(gtools)
library(stats4)
library(rmutil)
library(gsl)
library(invgamma)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(plotly)
library(knitr)
# library(rgl)
library(gtools)
library(stats4)
library(rmutil)
library(gsl)
library(invgamma)
```
